### 2023-07-11 manuscript.tex
Merge branch 'main' of github.com:habi/EAWAG-manuscript into main [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5520399868

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c6b7ff7c02d5425b675ce348cd38ac7a88cbfeb3}{habi/EAWAG-manuscript@c6b7ff7}
on July 11, 2023.

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/05e0c4de935ffd552c20ae7ff34db6d16ce5ca6d}{habi/EAWAG-manuscript@05e0c4d}
on July 11, 2023.
